\noindent\rule{13cm}{1.0pt}\\ \vspace{0.2cm} A Polynomial-time Reduction of the 3-SAT to the Quadratic Congruence and other Related Problems \noindent\rule{13cm}{0.8pt}

### 2017-11-20 paper/paper.tex
Final version.

Before we prove reductions, we first need to properly define the concepts we are going to use. We
shall define a Problem as a question that takes a set of objects as input and returns another set
of objects as output. There are many types of problems: decision problems, where the output is
restricted to yes or no (or true or false) answers; optimization problems, where the answer is
given by a particular element of a set such that such an object optimizes certain criteria; and
search problems, which is when the answer is an element of the set of output answers.

@@

It is natural to conclude that problems have a certain complexity attached to them. Furthermore, we
can provide several algorithms that give answers to our problems. In this case in particular we
know that sorting a vector is $\bigo(n\lg n)$ at best. Examples of algorithms for the above problem
are InsertSort, MergeSort and BubbleSort, with each one having different worst case complexities.
We next show a few examples of different types of problems:

@@

The Euclidean algorithm is an example of an algorithm that solves the gcd problem, with
$\bigo(\ln(\max\{a,b\}))$.

@@

This classic computer science problem turns out to be $\Theta(m\cdot n)$. Following Cook and
Karp's, we treat only the case for decision problems. One might think this severly restricts the
generality of complexity classes, but it is easy to see that one can treat optimization and search
problems as special cases of decision problems. We do this by restricting these problems into their
decision problem subproblems:

@@

For the next part we assume Turing machines to be already defined, as we wish to keep this section
brief, as the title says. We consider an algorithm a series of steps that can be performed by a
Turing machine. A problem is solvable in polynomial time if there exists an algorithm that takes a
polynomial number of steps on the size of the instance. We define an instance as a particular input
of a problem. In the $\gcd$ decision problem, we could take the tuple $(253, 37, 1)$ as an instance
of the input. Both the Euclidean algorithm and the optimal 2-dimension LCS algorithm run in
polynomial time on the size of the instance. However, the general case of the LCS algorithm is
$\bigo(2^{n_1})$, where $n_i$ is the length of the $i$-th string, and thus is not polynomial.

@@

Let $\Pi$ and $\Pi'$ be problems. A polynomial-time reduction from $\Pi$ to $\Pi'$ is an algorithm
that solves $\Pi$ using an algorithm that solves $\Pi'$ as a subroutine, and that, excluding its
subroutine, is polynomial on the size of its instance. We denote such a reduction by
$\Pi\leq_p\Pi'$ if there exists a polynomial reduction, from $\Pi$ to $\Pi'$.

@@

We can prove that SAT $\leq_p$ 3-SAT by turning the clauses in the SAT problem into 3-SAT
clauses~\cite{karp}. Recall Karp's 23 NP-complete list of problems. Each nesting means that the
nested item $\Pi'$ and its parent item $\Pi$ obey $\Pi\leq_p\Pi'$. The SAT problem, can also be
reduced to the Hamiltonian cycle problem by turning edges and vertices into SAT clauses. The vertex
cover problem can also be reduced to the Hamiltonian cycle problem~\cite{karp}.

@@

\begin{definition} A problem $\Pi$ is NP-hard if the existence of a polynomial algorithm for $\Pi$
  implies on $\p=\np$.
\end{definition}

@@

  Note how in all cases above, the clause is satisfiable if and only if $y_k\neq -1$. In the first
  case, when $y_k=-1$, no literal $x_i$ is valuated as true. In the second case, when $y_k\neq -1$,
  no literal $x_i$ is valuated as true and $\ov{x}_p$ is valuated as false. The third case is
  similar, with $x_t$ false, and $\ov{x}_p,\ov{x}_q$ false. For the last case, all $\ov{x}_i$ are
  set to false. When $y_k\neq -1$, there exists some literal being valuated as true, and therefore
  the clause $\sigma_k$ is valuated as true.

@@

Manders and Adleman proved in both~\cite{qcp1,qcp2} that not only the QCP is NP-complete, but also
the following:

>>>>

Before we prove reductions, we first need to properly define the concepts we are going to use. We
shall define a Problem as a question that takes a set of objects as input and returns another set
of objects as output. There are many types of problems: decision problems, where the output is
restricted to yes or no (or true or false) answers; search problems, when the output is an element
of the set; and optimization problems where the answer is given by a particular element of the set
that optimizes certain criteria.

@@

It is natural to conclude that problems have a certain complexity attached to them. Furthermore, we
can provide several algorithms that give answers to our problems. In this case in particular we
know that sorting a vector through comparison is $\bigo(n\lg n)$ at best. Examples of algorithms
for the above problem are InsertionSort, MergeSort and BubbleSort, with each one having different
worst case complexities.  We next show a few examples of different types of problems:
\newpage

@@

The Euclidean algorithm is an example of an algorithm that solves the gcd problem in
$\bigo(\ln(\max\{a,b\}))$.

@@

This classic computer science problem turns out to be $\Theta(m\cdot n)$. Following Cook and
Karp's, we treat only the case for decision problems. One might think this severly restricts the
generality of complexity classes, but it is easy to see that one can treat decision problems as
special cases of optimization and search problems. We do this by restricting these problems into
their decision problem subproblems:

@@

For the next part we assume Turing machines to be already defined, as we wish to keep this section
brief, as the title says. We consider an algorithm a series of finite steps that can be performed
by a Turing machine. A problem is solvable in polynomial time if there exists an algorithm that
takes a polynomial number of steps on the size of the instance. We define an instance as a
particular input of a problem. In the $\gcd$ decision problem, we could take the tuple $(253, 37,
1)$ as an instance of the input. Both the Euclidean algorithm and the optimal 2-dimension LCS
algorithm run in polynomial time on the size of the instance. However, the general case of the LCS
algorithm is $\bigo(2^{n_1})$, where $n_i$ is the length of the $i$-th string, and thus not
polynomial.

@@

Let $\Pi$ and $\Pi'$ be problems. A polynomial-time reduction from $\Pi$ to $\Pi'$ is an algorithm
that solves $\Pi$ using an algorithm that solves $\Pi'$ as a subroutine, and that (excluding its
subroutine) is polynomial on the size of its instance. We denote such a reduction by
$\Pi\leq_p\Pi'$ if there exists a polynomial reduction from $\Pi$ to $\Pi'$.

@@

We can prove that SAT $\leq_p$ 3-SAT by turning the clauses in the SAT problem into 3-SAT
clauses~\cite{karp}. Recall Karp's 23 NP-complete list of problems. Each nesting means that the
nested item $\Pi'$ and its parent item $\Pi$ obey $\Pi\leq_p\Pi'$. The SAT problem can also be
reduced to the Hamiltonian cycle problem by turning edges and vertices into SAT clauses. The vertex
cover problem can also be reduced to the Hamiltonian cycle problem~\cite{karp}.

@@

\begin{definition} A problem $\Pi$ is NP-hard if the existence of a polynomial algorithm for $\Pi$
  implies in $\p=\np$.
\end{definition}

@@

  Note how in all cases above, the clause is satisfiable if and only if $y_k\neq -1$. In the first
  case, when $y_k=-1$, no literal $x_i$ is evaluated as true. In the second case, when $y_k\neq -1$,
  no literal $x_i$ is evaluated as true and $\ov{x}_p$ is evaluated as false. The third case is
  similar, with $x_t$ false, and $\ov{x}_p,\ov{x}_q$ false. For the last case, all $\ov{x}_i$ are
  set to false. When $y_k\neq -1$, there exists some literal being evaluated as true, and therefore
  the clause $\sigma_k$ is evaluated as true.

@@

Manders and Adleman proved in both~\cite{qcp1,qcp2} that not only the QCP is NP-complete, but also
that
